% Markusos Resume/CV
% Compiled with XeLaTeX
% 01/02 - 2014

\documentclass{markusos-cv}

\begin{document}

\header{Markus}{Östberg}{Software Developer} 

%	Sidebar

\begin{aside}
\section{Contact}
Alphyddevägen 9
131 35 Nacka
Stockholm, Sweden
(+46) 76-849 05 38
~
\href{mailto:markusos@kth.se}{markusos@kth.se}
\href{http://www.csc.kth.se/~markusos}{csc.kth.se/\textasciitilde markusos}
\href{http://www.linkedin.com/in/markusos}{linkedin.com/in/markusos}
\href{https://github.com/markusos}{github.com/markusos}
\section{Languages}
Swedish
English
\section{Programming}
Java, C++
Python, PHP
JavaScript
HTML\&CSS
C\#, SQL
\section{Technical Skills}
Web Development
Algorithm Design
Problem Solving
Quality Assurance
Computer Security
\end{aside}

%	Education

\section{Education}

\begin{entrylist}
\entry
{2008 - 2013 \\}
{Stockholm, Sweden}
{KTH Royal Institute of Technology}
{Master of Science in Engineering}
{
Degree Programme in Computer Science and Engineering
\begin{itemize}
	\item Project highlights: 
	\begin{itemize}
		\item Bachelor’s Project: Explored how the algorithm parameters\\ in Genetic Algorithm affect the evolution.
		\item Software Engineering Project: Online live streaming and move\\ recording of chess games using DGT electronic chess boards. 
		\item Robotics and Autonomous Systems Project:\\ Built and implemented an autonomous robot that\\ could explore and map a labyrinth.
	\end{itemize}
\end{itemize}
}
\end{entrylist}

%	Experience

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{07/2013 - Present}
{Stockholm, Sweden}
{Trustly Group AB}
{Software Developer} 
{
\begin{itemize}
\item Responsible for bank integration in Trustly's payment transaction\\ system.
\item Technologies: Java, Selenium, Sikuli, PostgreSQL, GIT.
\end{itemize}
}
\\%------------------------------------------------
\entry
{01/2013 - 07/2013}
{Stockholm, Sweden}
{Findwise AB}
{Masters Thesis Worker} 
{
\begin{itemize}
\item Project Title: Subtopic extraction using graph based methods.
\item Explored subtopic extraction using search engine technology,\\ combined with graph centrality ranking of topic candidates.
\item Technologies: Java, ElasticSearch, MongoDB, REST, GIT.
\end{itemize} 
}
\\%------------------------------------------------
\entry
{06/2012 - 12/2012}
{Stockholm, Sweden}
{Zimzon AB}
{Software Developer\normalfont{, Summer Intern and part-time job}} 
{
\begin{itemize}
\item Implemented and integrated an web-based administration\\ system for management of access cards.
\item Developed a prototype of a system for online creation\\ and ordering of printed postcards.
\item Evaluated the use of ASP.NET MVC 4 for future projects.
\item Technologies: C\#, ASP.NET, HTML, CSS, JavaScript, jQuery.
\end{itemize} 
}
\\%------------------------------------------------
\entry
{06/2010 - 06/2012}
{Stockholm, Sweden}
{Tobii Technology AB}
{Quality Assurance Engineer\normalfont{, Summer Intern and part-time job}} 
{
\begin{itemize}
\item Quality Assurance testing of Tobii's eye tracker hardware\\ and software at the Tobii Assistive Technology department.
\item Responsibilities included integration and system testing,\\ using both use cases and exploratory methods.
\end{itemize} 
}
\\%------------------------------------------------
\entry
{10/2009 - 10/2010}
{Stockholm, Sweden}
{We Know IT Sweden}
{IT Support Consultant\normalfont{, Part-time job}} 
{
\begin{itemize}
\item Consulting assignments including: cleaning up viruses,\\ recovering lost data, installing printers and setting up local networks.
\item The work involved on-site installation and problem solving\\ at customers home or offices.
\end{itemize} 
}
%------------------------------------------------
\end{entrylist}
\end{document}